Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-25 inst/surfing_jsa_rebuttal_minorcomments.tex

\textcolor{blue}{Done}

Page 4: The authors mention the surfer Vries---who does not appear to
be a wildcard---whose maximum likelihood strength is zero. Why is
this? My guess is that Vries has never won a competitive surfing heat
(and therefore there is no information on his true, underlying
ability), however a brief clarification here woud be useful.

\textcolor{blue}{The referee is quite right: Vries competed only twice
  in 2019, coming last (second and third) in each of his two sessions.
  Brief explanation added to he mauscript.}

Page 6 / Figure 1: I'm pleased to see the authors replace the old pie
chart in Figure 1 with a dot chart---this is a much clearer
visualization of the results.  On Page 6 the authors state: ``Figure 1
shows the maximum likelihood estimate for the 23 competitors'
strengths, which appears to show a wide range from Florence at about
$17.5\%$ down to Morais at about $1\%$". What exactly do the
quantities $17.5\%$ and $1\%$ refer to/how are they computed? A quick
clarification of these quantities would help explain the practical
implications of the findings.

\textcolor{blue}{The figures are, as stated, the maximum likelihood
  estimates of the competitors' strengths.  We think that our use of
  percentages (which add to 100) instead of strengths (which add to 1)
  was the cause of the confusion and we have amended the manuscript to
  use strengths, not percentages.}

Page 7/Figure 2: The authors suggest there is a loose positive correlation between maximum likelihood
strength and total points, which is undoubtedly true. However, the x-axis on Figure 2 itself has been
distorted, which makes the trend appear more linear than it really is. I’d prefer to see the x-axis
undistorted, unless the authors are explicitly trying to make a point about the trend being log-linear,
in which case I’d like to see this briefly discussed.
Page 7: The authors suggest we may reject the hypothesis that the strength of the entity exceeds
about 0.025. Does this assertation come with a supporting p-value? It is unclear from Figure 4 how
this conclusion is reached.

### 2022-09-25 inst/surfing_jsa.tex
fixes #170

Figure~\ref{dotchartmax} shows the maximum likelihood estimate for the
23 competitors' strengths, which appears to show a wide range from
Florence at about 17.5\% down to Morais at about 1\%.  The {\tt
  hyper2} software~\citep{hankin2017_nomarkup} may be used to formally assess
one plausible null: that the competitors all have equal skill, that is
$H_0\colon p_\mathrm{Andino} = p_\mathrm{Bourez}=\ldots=
p_\mathrm{Wright}=\frac{1}{23}$, and any differences in placings are
due to random variation.  This test is performed by function {\tt
  equalp.test()} in the package which uses the method of support
\citep{edwards1992}.  The test rejects the null (in favour of the
evaluate) at $p=4\times 10^{-5}$.  There is thus strong evidence to
suggest that the competitors are indeed of different skills and the
result actually reflects genuine differences in abilities, rather than
the result of random chance.  Alternatively, we may view the dataset
as being sufficiently informative to reveal actual differences in
surfing ability.  Observe that the competitors' points (that is, the
final column of table~\ref{resultstable}) cannot be used for this type
of probabilistic analysis: the points awarded are arbitrary and
changing the points system would change the points scored but not
affect the competitors' behaviour.

>>>>

Figure~\ref{dotchartmax} shows the maximum likelihood estimate for the
23 competitors' strengths, which appears to show a wide range from
Florence at about $0.175$ down to Morais at about $0.01$.  The {\tt
  hyper2} software~\citep{hankin2017_nomarkup} may be used to formally assess
one plausible null: that the competitors all have equal skill, that is
$H_0\colon p_\mathrm{Andino} = p_\mathrm{Bourez}=\ldots=
p_\mathrm{Wright}=\frac{1}{23}$, and any differences in placings are
due to random variation.  This test is performed by function {\tt
  equalp.test()} in the package which uses the method of support
\citep{edwards1992}.  The test rejects the null (in favour of the
evaluate) at $p=4\times 10^{-5}$.  There is thus strong evidence to
suggest that the competitors are indeed of different skills and the
result actually reflects genuine differences in abilities, rather than
the result of random chance.  Alternatively, we may view the dataset
as being sufficiently informative to reveal actual differences in
surfing ability.  Observe that the competitors' points (that is, the
final column of table~\ref{resultstable}) cannot be used for this type
of probabilistic analysis: the points awarded are arbitrary and
changing the points system would change the points scored but not
affect the competitors' behaviour.
